---
title: "ch1"
output: github_document
---

String Manipulation in R with stringr
https://www.datacamp.com/courses/string-manipulation-in-r-with-stringr
Charlotte Wickham

# Quotes

`\`
: escape sequence
: backslash type `\\`

```{r}
library(tidyverse)
"\"There's plenty of room!\" said Alice indignantly, and she sat down in a large arm-chair at one end of the table." %>% cat
'"There\'s plenty of room!" said Alice indignantly, and she sat down in a large arm-chair at one end of the table.' %>% cat
```

# Emoji

```{r}
cat("hello\n\U1F30D")
```

`\U` followed by up to 8 hex digits sequence denotes a particular Unicode character.

1. using base 16 and the digits 0-9 and A-F. http://www.unicode.org/charts/
1. four digits for the codepoint, an alternative escape sequence is `\u`.

# number

感觉 fixed 和 scientific 好复杂。

1. 有效数字，使用`format(..., digits = n)`，小数点前后取最大数的数位和最小数的数位(解释看例子)
    1. 方便以列展示数据，但是当数据呈现是居中，可以用`trim = TRUE`去除效果。
1. 取消科学计数法，使用`format(..., scientific = FALSE)`

```{r}
# Some vectors of numbers
percent_change  <- c(4, -1.91, 3.00, -5.002)
income <-  c(72.19, 1030.18, 10291.93, 1189192.18)
p_values <- c(0.12, 0.98, 0.0000191, 0.00000000002)

# Format c(0.0011, 0.011, 1) with digits = 1
format(c(0.0011, 0.011, 1), digits = 1)

# Format c(1.0011, 2.011, 1) with digits = 1
format(c(1.0011, 2.011, 1), digits = 1)

# Format percent_change to one place after the decimal point
format(percent_change, digits = 2)

# Format income to whole numbers
format(income, digits = 2)
# stretch the small number

# Format p_values in fixed format
format(p_values, scientific = FALSE)
```

1. 三位数控制，使用`big.mark = ','`给出分隔符，`big.interval = 3`给出分割距离。

```{r}
formatted_income <- format(income, digits = 2)

# Print formatted_income
formatted_income

# Call writeLines() on the formatted income
writeLines(formatted_income)

# Define trimmed_income
trimmed_income <- format(income, digits =2, trim = TRUE)

# Call writeLines() on the trimmed_income
writeLines(trimmed_income)

# Define pretty_income
pretty_income <- format(income, digits = 2, big.mark = ",",big.interval = 4)
# 中文需要四位分隔符

# Call writeLines() on the pretty_income
writeLines(pretty_income)
```

# formatC

based on C style syntax

1. `"f"` for fixed, `digits` is the number of digits after the decimal point.
1. `"e"` for scientific, and
1. `"g"` for fixed unless scientific saves space


1. `flag = "+"`表示数据正负号
1. `format = "g", digits = 2`用最少字母表示小数点后两位
1. `flag = "0"`前面用0 pad 上，不清晰，也使用`str_pad`替代

```{r}
# From the format() exercise
x <- c(0.0011, 0.011, 1)
y <- c(1.0011, 2.011, 1)

# formatC() on x with format = "f", digits = 1
formatC(x, format = "f", digits = 1)
format(x, digits = 1)
# formatC() on y with format = "f", digits = 1
formatC(y, format = "f", digits = 1) 
format(y, format = "f", digits = 1)

# Format percent_change to one place after the decimal point
formatC(percent_change, format = "f", digits = 1)

# percent_change with flag = "+"
formatC(percent_change, format = "f", digits = 1, flag = "+")

# Format p_values using format = "g" and digits = 2
formatC(p_values, format = "g", digits = 2)
```

```{r}
formatC(income,digits = 0,format = 'f',flag = '0')
```

1. 会计格式展示，使用`format`和`paste`完成
1. `justify = "right"`可以让文本居中或者向左向右。

```{r}
# Define the names vector
income_names <- c("Year 0", "Year 1", "Year 2", "Project Lifetime")

# Create pretty_income
pretty_income <- format(income, digit = 2, big.mark = ',')

# Create dollar_income
dollar_income <- paste('$', pretty_income, sep = '')

# Create formatted_names
formatted_names <- format(income_names, justify = "right")

# Create rows
rows <- paste(formatted_names, dollar_income, sep = '   ')

# Write rows
writeLines(rows)
```

```{r}
income %>% 
    round %>% 
    as.character %>% 
    str_pad(string = .,width = max(str_count(.)),pad = '0')
formatC(income, width = 7, format = "d", flag = "0")
```

1. `formatC`更简单一些
([Richie Cotton](https://stackoverflow.com/questions/5812493/how-to-add-leading-zeros))
1. 可以方便用于文件命名

```{r}
0:999 %>% 
    as.character %>% 
    str_pad(string = .,width = max(str_count(.)),pad = '0') %>% 
    head
```

