---
title: "ch4 - rebus"
output: github_document
---

# capture + str_match

配合`str_match`使用

```{r}
library(tidyverse)
library(rebus)
hero_contacts <- 
    c("(wolverine@xmen.com)","wonderwoman@justiceleague.org","thor@avengers.com")
capture(one_or_more(WRD)) %R% 
    "@" %R% 
    capture(one_or_more(WRD)) %R% 
    DOT %R% 
    capture(one_or_more(WRD)) %>% 
    str_match(hero_contacts,.)
```

capture 的特性也见于 impala 的函数 `regexp_extract`

但是邮箱正则化很难提取，见
[讨论](https://stackoverflow.com/questions/201323/how-to-validate-an-email-address-using-a-regular-expression/201378#201378)

<details>
<summary>另外一个例子</summary>

```{r}
narratives <- 
c("19YOM-SHOULDER STRAIN-WAS TACKLED WHILE PLAYING FOOTBALL W/ FRIENDS ","31 YOF FELL FROM TOILET HITITNG HEAD SUSTAINING A CHI ","ANKLE STR. 82 YOM STRAINED ANKLE GETTING OUT OF BED ","TRIPPED OVER CAT AND LANDED ON HARDWOOD FLOOR. LACERATION ELBOW, LEFT. 33 YOF*","10YOM CUT THUMB ON METAL TRASH CAN DX AVULSION OF SKIN OF THUMB ","53 YO F TRIPPED ON CARPET AT HOME. DX HIP CONTUSION ","13 MOF TRYING TO STAND UP HOLDING ONTO BED FELL AND HIT FOREHEAD ON RADIATOR DX LACERATION","14YR M PLAYING FOOTBALL; DX KNEE SPRAIN ","55YOM RIDER OF A BICYCLE AND FELL OFF SUSTAINED A CONTUSION TO KNEE ","5 YOM ROLLING ON FLOOR DOING A SOMERSAULT AND SUSTAINED A CERVICAL STRA IN")
```

```{r}
# narratives has been pre-defined
narratives

# Add capture() to get age, unit and sex
pattern <- capture(optional(DGT) %R% DGT) %R%  
  optional(SPC) %R% capture(or("YO", "YR", "MO")) %R%
  optional(SPC) %R% capture(or("M", "F"))

# Pull out from narratives
str_match(narratives,pattern)
```

</details>


<details>
<summary>同时优化一下，只提取首字母表示年月</summary>


```{r}
# Edit to capture just Y and M in units
pattern2 <- capture(optional(DGT) %R% DGT) %R%  
  optional(SPC) %R% capture(or("Y", "M")) %R% optional(or("O","R")) %R%
  optional(SPC) %R% capture(or("M", "F"))

# Check pattern
str_view(narratives, pattern2)

# Pull out pieces
str_match(narratives, pattern2)
```


</details>

# backreferences

1. 方便删除重复单词
1. 使用引用进行正序和反序提取字符
    1. <input type="checkbox" id="checkbox1" class="styled">这一波可以去stackoverflow回复很多问题了
    
```{r}
str_sub(c("hello", "sweet", "kitten"), 
  pattern = capture(LOWER) %R% REF1)
```

这里相当于`LOWER %R% LOWER`

abab

```{r}
# Names with a pair of repeated letters
pair_of_repeated <- capture((LOWER %R% LOWER)) %R% REF1

# Test it
str_view('abab', pattern = pair_of_repeated, match = TRUE)
```

abba

```{r}
# Names with a pair that reverses
pair_that_reverses <- capture(LOWER) %R% capture(LOWER) %R% REF2 %R% REF1

# Test it
str_view('abba', pattern = pair_that_reverses, match = TRUE)
```

精确匹配

```{r}
# Four letter palindrome names
four_letter_palindrome <- exactly(
  capture(LOWER) %R% capture(LOWER) %R% REF2 %R% REF1
)

# Test it
str_view('abba', pattern = four_letter_palindrome, match = TRUE)
```

```{r}
# View text containing phone numbers
contact <- 
c('Call me at 555-555-0191','123 Main St','(555) 555 0191','Phone: 555.555.0191 Mobile: 555.555.0192')


# Replace digits with "X"
str_replace(contact, DGT, "X")

# Replace all digits with "X"
str_replace_all(contact, DGT, "X")

# Replace all digits with different symbol
str_replace_all(contact, DGT, c("X", ".", "*", "_"))
```

这是`str_replace_all`的特性，函数向量化。

剔除重复的词

```{r}
str_replace_all(
    'I am the the aquaman'
    ,SPC %R% 
        capture(one_or_more(WRD)) %R% 
        SPC %R% 
        REF1
    ,' ' %R% REF1)
```


这个可以在RStudio，replace的时候，可以每个替换对应的值

```{r}
SPC %R% 
    capture(one_or_more(WRD)) %R% 
    SPC %R% 
    REF1
```

表示

```{r}
SPC %R% 
    capture(one_or_more(WRD)) %R% 
    SPC %R% 
    capture(one_or_more(WRD))
```

```{r}
adverbs <- 
c("ABNORMALLY","ABSENTMINDEDLY","ACCIDENTALLY","ACIDLY","ACTUALLY","ADVENTUROUSLY","AFTERWARDS","ALMOST","ALWAYS","ANGRILY","ANNUALLY","ANXIOUSLY","ARROGANTLY","AWKWARDLY","BADLY","BASHFULLY","BEAUTIFULLY","BITTERLY","BLEAKLY","BLINDLY","BLISSFULLY","BOASTFULLY","BOLDLY","BRAVELY","BRIEFLY","BRIGHTLY","BRISKLY","BROADLY","BUSILY","CALMLY","CAREFULLY","CARELESSLY","CAUTIOUSLY","CERTAINLY","CHEERFULLY","CLEARLY","CLEVERLY","CLOSELY","COAXINGLY","COLORFULLY","COMMONLY","CONTINUALLY","COOLLY","CORRECTLY","COURAGEOUSLY","CROSSLY","CRUELLY","CURIOUSLY","DAILY","DAINTILY","DEARLY","DECEIVINGLY","DEEPLY","DEFIANTLY","DELIBERATELY","DELIGHTFULLY","DILIGENTLY","DIMLY","DOUBTFULLY","DREAMILY","EASILY","ELEGANTLY","ENERGETICALLY","ENORMOUSLY","ENTHUSIASTICALLY","EQUALLY","ESPECIALLY","EVEN","EVENLY","EVENTUALLY","EXACTLY","EXCITEDLY","EXTREMELY","FAIRLY","FAITHFULLY","FAMOUSLY","FAR","FAST","FATALLY","FEROCIOUSLY","FERVENTLY","FIERCELY","FONDLY","FOOLISHLY","FORTUNATELY","FRANKLY","FRANTICALLY","FREELY","FRENETICALLY","FRIGHTFULLY","FULLY","FURIOUSLY","GENERALLY","GENEROUSLY","GENTLY","GLADLY","GLEEFULLY","GRACEFULLY","GRATEFULLY","GREATLY","GREEDILY","HAPPILY","HASTILY","HEALTHILY","HEAVILY","HELPFULLY","HELPLESSLY","HIGHLY","HONESTLY","HOPELESSLY","HOURLY","HUNGRILY","IMMEDIATELY","INNOCENTLY","INQUISITIVELY","INSTANTLY","INTENSELY","INTENTLY","INTERESTINGLY","INWARDLY","IRRITABLY","JAGGEDLY","JEALOUSLY","JOSHINGLY","JOVIALLY","JOYFULLY","JOYOUSLY","JUBILANTLY","JUDGEMENTALLY","JUSTLY","KEENLY","KIDDINGLY","KINDHEARTEDLY","KINDLY","KISSINGLY","KNAVISHLY","KNOTTILY","KNOWINGLY","KNOWLEDGEABLY","KOOKILY","LAZILY","LESS","LIGHTLY","LIKELY","LIMPLY","LIVELY","LOFTILY","LONGINGLY","LOOSELY","LOUDLY","LOVINGLY","LOYALLY","MADLY","MAJESTICALLY","MEANINGFULLY","MECHANICALLY","MERRILY","MISERABLY","MOCKINGLY","MONTHLY","MORE","MORTALLY","MOSTLY","MYSTERIOUSLY","NATURALLY","NEARLY","NEATLY","NEEDILY","NERVOUSLY","NEVER","NICELY","NOISILY","NOT","OBEDIENTLY","OBNOXIOUSLY","ODDLY","OFFENSIVELY","OFFICIALLY","OFTEN","ONLY","OPENLY","OPTIMISTICALLY","OVERCONFIDENTLY","OWLISHLY","PAINFULLY","PARTIALLY","PATIENTLY","PERFECTLY","PHYSICALLY","PLAYFULLY","POLITELY","POORLY","POSITIVELY","POTENTIALLY","POWERFULLY","PROMPTLY","PROPERLY","PUNCTUALLY","QUAINTLY","QUARRELSOMELY","QUEASILY","QUEERLY","QUESTIONABLY","QUESTIONINGLY","QUICKER","QUICKLY","QUIETLY","QUIRKILY","QUIZZICALLY","RAPIDLY","RARELY","READILY","REALLY","REASSURINGLY","RECKLESSLY","REGULARLY","RELUCTANTLY","REPEATEDLY","REPROACHFULLY","RESTFULLY","RIGHTEOUSLY","RIGHTFULLY","RIGIDLY","ROUGHLY","RUDELY","SADLY","SAFELY","SCARCELY","SCARILY","SEARCHINGLY","SEDATELY","SEEMINGLY","SELDOM","SELFISHLY","SEPARATELY","SERIOUSLY","SHAKILY","SHARPLY","SHEEPISHLY","SHRILLY","SHYLY","SILENTLY","SLEEPILY","SLOWLY","SMOOTHLY","SOFTLY","SOLEMNLY","SOLIDLY","SOMETIMES","SOON","SPEEDILY","STEALTHILY","STERNLY","STRICTLY","SUCCESSFULLY","SUDDENLY","SURPRISINGLY","SUSPICIOUSLY","SWEETLY","SWIFTLY","SYMPATHETICALLY","TENDERLY","TENSELY","TERRIBLY","THANKFULLY","THOROUGHLY","THOUGHTFULLY","TIGHTLY","TOMORROW","TOO","TREMENDOUSLY","TRIUMPHANTLY","TRULY","TRUTHFULLY","ULTIMATELY","UNABASHEDLY","UNACCOUNTABLY","UNBEARABLY","UNETHICALLY","UNEXPECTEDLY","UNFORTUNATELY","UNIMPRESSIVELY","UNNATURALLY","UNNECESSARILY","UPBEAT","UPLIFTINGLY","UPRIGHT","UPSIDE-DOWN","UPWARD","UPWARDLY","URGENTLY","USEFULLY","USELESSLY","USUALLY","UTTERLY","VACANTLY","VAGUELY","VAINLY","VALIANTLY","VASTLY","VERBALLY","VERY","VICIOUSLY","VICTORIOUSLY","VIOLENTLY","VIVACIOUSLY","VOLUNTARILY","WARMLY","WEAKLY","WEARILY","WELL","WETLY","WHOLLY","WILDLY","WILLFULLY","WISELY","WOEFULLY","WONDERFULLY","WORRIEDLY","WRONGLY","YAWNINGLY","YEARLY","YEARNINGLY","YESTERDAY","YIELDINGLY","YOUTHFULLY")
```

随机给动词增加副词

```{r}
# Build pattern to match words ending in "ING"
pattern <- one_or_more(WRD) %R% "ING"
str_view(narratives, pattern)

# Test replacement
str_replace(narratives, capture(pattern), 
  str_c("CARELESSLY", REF1, sep = " "))

# One adverb per narrative
adverbs_10 <- sample(adverbs, 10)

# Replace "***ing" with "adverb ***ly"
str_replace(narratives, 
  capture(pattern),
  str_c(adverbs_10, REF1, sep = " "))  
```

>
Replacement combined with backreferences can be really useful for reformatting text data.

书签

https://campus.datacamp.com/courses/string-manipulation-in-r-with-stringr/more-advanced-matching-and-manipulation?ex=9
