---
title: "ch5-case-study"
author: Jiaxiang Li
date: "`r Sys.Date()`"
bibliography: ../refs/add.bib
---

```{r message=FALSE, warning=FALSE}
source(here::here("code/load.R"))
```


参考 @Charlotte_Wickham2019

```{r}
library(stringi)
suppressMessages(library(tidyverse))
library(rebus)
earnest_file <- 'data/importance-of-being-earnest.txt'
```

<input type="checkbox" id="checkbox1" class="styled">这个老师的文本处理非常优秀，应该 follow

的确是针对小说进行过分析。

```{r}
# Read play in using stri_read_lines()
earnest <- stri_read_lines(earnest_file)

# Detect start and end lines
start <- str_which(earnest, fixed("START OF THE PROJECT"))
end <- str_which(earnest, fixed("END OF THE PROJECT"))

# Get rid of gutenberg intro text
earnest_sub  <- earnest[(start + 1):(end - 1)]

# Detect first act
lines_start <- str_which(earnest_sub, fixed("FIRST ACT"))

# Set up index
intro_line_index <- 1:(lines_start - 1)

# Split play into intro and play
intro_text <- earnest_sub[intro_line_index]
play_text <- earnest_sub[-intro_line_index]

# Take a look at the first 20 lines
writeLines(play_text[1:20])
```

[Why does Charlotte Wickham says `stri_read_lines()` is better than `readLines()`?](https://community.rstudio.com/t/why-does-charlotte-wickham-says-stri-read-lines-is-better-than-readlines/19920?u=econkid)


提供了处理文本的函数，而不需要在`data.frame`去实现。

```{r}
# Get rid of empty strings
empty <- stri_isempty(play_text)
play_lines <- play_text[!empty]
```

```{r}
play_lines[10:15]
```

```{r}
# Pattern from last step
pattern_2 <- START %R% ascii_upper() %R% one_or_more(WRD) %R% DOT

# Get subset of lines that match
lines <- str_subset(play_lines,pattern_2)

# Extract match from lines
who <- str_extract(lines,pattern_2)

# Let's see what we have
unique(who)
```

[stri_read_lines  更好 总结一下](https://community.rstudio.com/t/why-does-charlotte-wickham-says-stri-read-lines-is-better-than-readlines/19920)

>
`or` takes multiple character vector inputs and returns a character vector of the inputs separated by pipes. `%|%` is an operator interface to this function. `or1` takes a single character vector and returns a string collapsed by pipes.

```{r}
# Variables from previous step
characters <- c("Algernon", "Jack", "Lane", "Cecily", "Gwendolen", "Chasuble", 
  "Merriman", "Lady Bracknell", "Miss Prism")
pattern_3 <- START %R% or1(characters) %R% DOT

# Pull out matches
lines <- str_subset(play_lines, pattern_3)

# Extract match from lines
who <- str_extract(lines, pattern_3)

# Let's see what we have
unique(who)

# Count lines per character
table(who)
```

`Jack and Algernon [Speaking together.]`这个问题需要解决。

<input type="checkbox" id="checkbox1" class="styled">这个的处理不够strong，我需要知道每一步发生的逻辑，这样之后才能精进

# ignore case

```{r}
library(readr)
catcidents <- read_rds('data/catcidents.rds')
```

```{r}
# catcidents has been pre-defined
head(catcidents)

# Construct pattern of DOG in boundaries
whole_dog_pattern <- whole_word("DOG")

# See matches to word DOG
str_view(catcidents,whole_dog_pattern,match=T)
```

```{r}
x <- c("Cat", "CAT", "cAt") 
str_subset(x, "cat")
str_subset(x, stringr::regex("cat", ignore_case = TRUE))
```

# stri_trans_totitle() 

```{r}
library(stringi)

# Get first five catcidents
cat5 <- catcidents[1:5]

# Take a look at original
writeLines(cat5)

# Transform to title case
str_to_title(cat5)

# Transform to title case with stringi
stri_trans_totitle(cat5)

# Transform to sentence case with stringi
stri_trans_totitle(cat5,type = 'sentence')
```

<input type="checkbox" id="checkbox1" class="styled">整理下笔记，真的非常有用的学习

<input type="checkbox" id="checkbox1" class="styled">ppt 上面推荐的书，可以看一下

# 完成证书

参考 [DataCamp](https://www.datacamp.com/statement-of-accomplishment/course/c1fa2350565dc69c5e05822e053bd98e097674cf)

<iframe name="Jiaxiang Li" src="../refs/certificate.pdf" style='height: 100%; width: 100%;' frameborder="0" scrolling="yes" id="iframe">...</iframe>