# escape

[Stringr vignette Regular expressions]: https://stringr.tidyverse.org/articles/regular-expressions.html

```{r}
library(stringr)
```


> regexps use the backslash, `\`, to escape special behaviour. ([Stringr vignette Regular expressions])

escape 是这个意思。

Linux 系统中 `grep -E`，`E`就是 escape。
这样就不需要加 `\`。

> Unfortunately this creates a problem. We use strings to represent regular expressions, and `\` is also used as an escape symbol in strings. So to create the regular expression \. we need the string `"\\."`. ([Stringr vignette Regular expressions])

```{r collapse=TRUE}
# To create the regular expression, we need \\
dot <- "\\."

# But the expression itself only contains one:
writeLines(dot)
#> \.

# And this tells R to look for an explicit .
str_extract(c("abc", "a.c", "bef"), "a\\.c")
#> [1] NA    "a.c" NA
```


> If `\` is used as an escape character in regular expressions, how do you match a **literal `\`**? Well you need to escape it, creating the **regular expression `\\`**. To create that regular expression, you need to use a string, which also needs to escape `\`. That means to match a literal `\` you need to **write `"\\\\"`** — you need four backslashes to match one! ([Stringr vignette Regular expressions])

```{r collapse=TRUE}
x <- "a\\b"
writeLines(x)
#> a\b

str_extract(x, "\\\\")
#> [1] "\\"
```

> In this vignette, I use **`\`**. to denote the regular expression, and **`"\\."`** to denote the string that represents the regular expression. ([Stringr vignette Regular expressions])

regular expression 和 string to represent 是不一样的。

```{r echo=FALSE,fig.cap="escape 三种情况的举例"}
DiagrammeR::grViz('digraph asde91 {ranksep=.75; size = "7.5,7.5";{
		node [shape=plaintext, fontsize=16];

		/* the time-line graph */
		Literal -> "Regular Expression" -> "Write Representation";


	} { rank = same;}; 
	"." -> "\\\\." -> "“\\\\\\\\.”"
	
	"\\\\" -> "\\\\\\\\" -> "“\\\\\\\\\\\\\\\\”"
	
	"a\\\\\\\\b" -> "a\\\\\\\\\\\\\\\\b" -> "“a\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\b”"
	
}')
```

